
\documentclass[margin,line,sans,10pt]{res}

\newcommand{\myfont}{\fontsize{11pt}{11pt}\selectfont}

%\renewcommand{\ttdefault}{pcr}
\renewcommand*{\namefont}{\Huge\bfseries\upshape}
\renewcommand*{\sectionfont}{\myfont}

\RequirePackage{tgpagella}
\renewcommand*{\familydefault}{\rmdefault}
% yulunzhang's code
\usepackage{fancyhdr}
\usepackage{textcomp}
\pagestyle{plain}
\pagenumbering{arabic}
% yulunzhang's code
\usepackage{hyperref}
\usepackage{color}
%\hypersetup{
%   colorlinks=true,       % false: boxed links; true: colored links
%   linkcolor=red,          % color of internal links
%   citecolor=green,        % color of links to bibliography
%   filecolor=magenta,      % color of file links
%   urlcolor=blue,           % color of external links
%}

%\hypersetup{pdfborderstyle={/S/U/W 1}}
%\hypersetup{pdfborderstyle={/S/D/D[3 2]/W 1}}

\usepackage{url}

\usepackage{marvosym}
\usepackage{pifont}

\hyphenpenalty=750

\oddsidemargin -.41in \evensidemargin -1in \textwidth=5.7in
\textheight 9in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0.05in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{{\small$\bullet$}}{%
      \setlength{\itemsep}{0.05in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}


\name{{\namefont CHUANMIN JIA} \vspace*{.1in}}

\begin{resume}
\section{\sc Contact}
\vspace{.05in}
%Centre for Multimedia and Network Technology \\
%School of Computer Engineering, Nanyang Technological University\\
%N4-B2C-06, 50 Nanyang Avenue, Singapore 639798  \\
%{\Mobilefone~+65-90884656}\\
%{\Letter~\href{mailto:wli1@e.ntu.edu.sg}{\texttt{wli1@e.ntu.edu.sg}}}
%\begin{tabular}{@{}p{4.205in}p{1.33in}}
%Centre for Multimedia and Network Technology & \rightline{\Mobilefone~+65-90884656}\\
%School of Computer Engineering & %\rightline{\Letter~\href{mailto:wli1@e.ntu.edu.sg}{\texttt{wli1@e.ntu.edu.sg}}}\\
%Nanyang Technological University \\
%N4-B2C-06, 50 Nanyang Avenue, Singapore 639798  \\
%\href{https://sites.google.com/site/xyzliwen/}{\texttt{https://sites.google.com/site/xyzliwen/}}\\
%\end{tabular}

\begin{tabular}{@{}p{4.205in}p{1.33in}}
Institute of Digital Media, \rightline{\Letter~\href{mailto:cmjia@pku.edu.cn}{\texttt{cmjia@pku.edu.cn}}}\\
S2728, School of EE \& CS, Peking University, \\
Haidian District, Beijing 100871, China \\
{\href{http://http:www.jiachuanmin.site}{\texttt{http://www.jiachuanmin.site}}}\\
{\href{https://scholar.google.com/citations?user=x5Na9n0AAAAJ&hl=zh-CN}{\texttt{Google Scholar}}}\\

\end{tabular}

\section{\sc Research Interests}
\begin{list2}
\item{Video Processing}
\item{Light Field Image Compression}
\item{Machine Learning}

\end{list2}

\section{\sc Education}
{\bf New York University (NYU)} , New York, U.S. \hfill {Dec. 2017 -- present}
% \vspace{-.3cm}
\begin{list2}
\item{Visiting Scholar}
\item{{Advisor: Prof. Yao Wang} }
\end{list2}
\vspace{.1cm}

{\bf Peking University (PKU)} , Beijing, China \hfill {Sep. 2015 -- present}
% \vspace{-.3cm}
\begin{list2}
\item{{\em Ph.D.} candidate in Computer Science}
\item{{Advisor: Prof. Siwei Ma and Prof. Wen Gao} }
\end{list2}
\vspace{.1cm}

{\bf Beijing Univ. of Posts. \& Telecom. (BUPT)} , Beijing, China \hfill {Sep. 2011 -- Jul. 2015}
% \vspace{-.3cm}
\begin{list2}
\item{{\em B.Eng} in Computer Science and Technology }
\item{Overall GPA 86.7/100, rank: 10\%}
\item{Thesis: Research on Compressed Video Enhancement and GPU Acceleration. (in Chinese)}
\end{list2}
\vspace{.1cm}

\section{\sc Research Experience}

{\bf   Tandon School of Engineering}, New York University \hfill {Dec. 2017 -- present}
\begin{list2}
\item{{\em Research Assistant}}
\end{list2}
 \vspace{.1cm}
{\bf   Institute of Digital Media}, Peking University \hfill {Sep. 2014 -- present}
\begin{list2}
\item{{\em Research Assistant}}
\end{list2}
 \vspace{.1cm}
{\bf  Institute of Computational Linguistics}, Peking University \hfill {Feb. 2014 -- Aug. 2014}
\begin{list2}
\item{{\em Research Intern}}
\end{list2}
 \vspace{.1cm}
{\bf Innovation Research Center}, Beijing Univ. of Posts. \& Telecom. \hfill {Aug. 2013 -- Mar. 2014}
\begin{list2}
\item{{\em Research Intern }}
\end{list2}
 \vspace{.1cm}


\section{\sc Journal Papers}
% 1
\begin{list2}
\item{Siwei Ma, Xinfeng Zhang, Jian Zhang, \underline{\bf C. Jia}, Shiqi Wang and Wen Gao ``Nonlocal In-Loop Filter: The Way Toward Next-Generation Video Coding?," {\em {IEEE} MultiMedia} 23 (2), 16-26.}
\end{list2}
\vspace{.1cm}

%\begin{list2}
%\item{Yongbing Zhang, \underline{\bf Yulun Zhang$^*$}, Jian Zhang, and Qionghai Dai, ``Multiscale Adaptive Local Nonparametric Regression for Fast Single Image Super-Resolution," {\em submitted to {IEEE} Signal Process. Lett. (\textbf{SPL})}, {\bf under peer review}. ($^*$ corresponding author)}
%\end{list2}


\section{\sc Conference Papers}
\begin{list2}
%
\item{\underline{\bf C. Jia}, S. Wang, X. Zhang, S. Wang and S. Ma, ``Spatial-Temporal Residue Network Based In-Loop Filter for Video Coding", {\em {\bf Accepted} by IEEE Visual Communications and Image Processing ({\bf VCIP})}, St. Petersburg, Florida, USA, Dec, 2017. (Oral)}

%
\item{\underline{\bf C. Jia}, Y. Yang, X. Zhang, S. Wang, S. Wang and S. Ma, ``Light Field Image Compression with Sub-apertures Reordering and Adaptive Reconstruction", {\em Proc. of the Pacific-Rim Conference on Multimedia ({\bf PCM}}), Harbin, China, Sept, 2017. (Oral)} ({\bf{\color{red} Best Paper Award}})

%
\item{\underline{\bf C. Jia}, Y. Yang, X. Zhang, S. Wang, X. Zhang, S. Wang and S. Ma, ``Optimized Inter-view Prediction Based Light Field Image Compression with Adaptive Reconstruction", {\em Proc. of IEEE International Conference on Image Processing ({\bf ICIP}}), grand challenge for LF image coding, Beijing, China, Sept, 2017. (Oral)}

%
\item{\underline{\bf C. Jia}, X. Zhang, J. Zhang, S. Wang and S. Ma, ``Deep Convolutional Network based Image Quality Enhancement for Low Bit Rate Image Compression," {\em Proc. of IEEE Visual Communications and Image Processing ({\bf VCIP})}, Chengdu, China, Nov. 2016. (Oral)}

\vspace{.1cm}
%
\item{J. Zhang, \underline{\bf C. Jia},  N. Zhang, S. Ma, and W. Gao, ``Structure-driven Adaptive Non-local Filter for High Efficiency Video Coding (HEVC)," {\em Proc. of IEEE Data Compression Conference ({\bf DCC})}, Snowbird, Utah, USA, Mar. 2016. (Oral) ({\bf Top Conference in Data Compression})}

\vspace{.1cm}
%
\item{J. Zhang, \underline{\bf C. Jia}, S. Ma, and W. Gao, ``Non-Local Structure-Based Filter for Video Coding," {\em Proc. of IEEE International Symposium on Multimedia ({\bf ISM})}, Miami, Florida, USA, Dec. 2015. (Oral)}

\end{list2}


\vspace{.1cm}
%\section{\sc Submissions}
%\begin{list2}
%\item{{\bf Wen Li} \emph{etal.}, ``Anonymous Submssion," {\em submitted to European Conference on Computer Vision (ECCV)}, 2014.}
%\item{Somebody, {\bf Wen Li} \emph{etal.}, ``Anonymous Submssion," {\em submitted to European Conference on Computer Vision (ECCV)}, 2014.}
%\item{Xinxing Xu$^*$, {\bf Wen Li}$^*$, Ivor W. Tsang, and Dong Xu, ``Multi-view Ambiguous Learning using Co-Labeling," {\em submitted to IEEE Transactions on Pattern Analysis and Machine Intelligence (T-PAMI)}} ($^*$ equal contributions).
%\end{list2}

%\item{Image Sampling, Coding and Reconstruction based on Compressive Sensing Theory, $\yen 190,000$, National Natural Science Foundation of China, 2016/1 ¨C- 2016/12.}
%\item{Conference Reviewer for ICME 2014, ICME2013, IJCAI2013, ACM-MM2013}
%\item{Journal Reviewer for International Journal of Computer Vision (IJCV), IEEE Transactions on %Neural Networks and Learning Systems (T-NNLS), IEEE Transactions on Systems, Man, and Cybernetics: %Part B (T-SMC-B), Machine Vision and Applications (MVAP), Signal Processing (SP)}


\vspace{0.8mm}
\section{\sc Honors and Awards}
\begin{list2}
\item{ {\bf Best Paper Award} of the Pacific-Rim Conference on Multimedia (PCM) conference, \hfill 2017}
\item{${1}^{st}$ prize of Video Big Data Compression Contest of the
       National Graduate Contest on Smart-City Technology. \hfill 2016}
\item{Excellent Graduation Thesis Award, Beijing Univ. of Posts. \& Telecom. \hfill 2015}
\item{Innovation Scholarship (Collaborative Innovation Center for Future Media Network). \hfill 2015}
\item{Honorable Mention Winner in American Mathematical Contest in Modeling. \hfill 2014}

\end{list2}

\section{\sc Professional Activity}
\vspace{-.4cm}
\subsection{\sc Reviewer}
\begin{list2}
\item{IEEE International Symposium on Multimedia (ISM). (since Aug 2017)}
\item{IEEE Visual Communication and Image Processing (VCIP). (since July 2017)}
\item{Journal of Visual Communication and Image Representation (JVCIR). (since Oct  2016)}
\end{list2}

\vspace{-.3cm}
\subsection{\sc Conference Oral Presentations and Invited Talks}
\begin{list2}
\item{Light Field Image Compression with Sub-apertures Reordering and Adaptive Reconstruction, {\em PCM2017, Harbin, China, Sep. 2017}}
\item{Optimized Inter-View Prediction Based Light Field Image Compression With Adaptive Reconstruction, {\em ICIP2017, Grand Challenge for Light Field Image coding, Beijing, China, Sep. 2017}}
\item{Deep Convolutional Network based Image Quality Enhancement for Low Bit Rate Image Compression, {\em VCIP2016, Chengdu, China, Nov. 2016}}

\end{list2}

\vspace{-.3cm}
\subsection{\sc Memberships}
\begin{list2}
\item{Student Member, IEEE}
\end{list2}

\section{\sc Selected Projects}
\begin{list2}
\begin{subsection}{\normalsize View Synthesis Optimization, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  Apr. 2016 - Sep. 2016}
    \item{Optimizing an open-source view synthesis software using CUDA. Achieving 6x acceleration, with real time FHD (1080P) view synthesis over 40fps.}
\end{subsection}
\begin{subsection}{\normalsize NFC Tour Guide, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  Aug. 2013 - Mar. 2014}
    \item{Developed an Android app using NFC for tourism. Mainly responsible for implementing of NFC pay, speech tour guide and database interface design.}
\end{subsection}
\begin{subsection}{\normalsize Flower Recognition, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  Jul. 2013 - Sep. 2013}
    \item{Proposed recognition algorithm by combining histogram and contour feature with linear classifier.
          iOS app development and recognition algorithm implementation.}
\end{subsection}
\end{list2}


\section{\sc Skills}
\begin{list2}
\item{Programming: C/C++, CUDA, MATLAB, Power Shell, Python, \LaTeX.}
\item{Operating System: Mac OS X, Ubuntu Linux, Windows}
\item{Libraries/Frameworks: Caffe, MXNET, Tensorflow, HEVC/H.265, AVS2}
\item{Github Repo: {\href{https://github.com/codersadis}{\texttt{https://github.com/codersadis}}} }
\end{list2}



\begin{center}
\textit{Last updated: October 9th 2017}

\end{center}
\end{resume}
\end{document}
